---
title: "Analysis of the mtcars Dataset"
author: "Michael Amakoh"
date: "10.03.2023"
output:
  slidy_presentation: default
  html_document:
    number_sections: yes
    toc: yes
  ioslides_presentation: default
mode: selfcontained
job: Reproducible Pitch Presentation
subtitle: Variables and MPG
highlighter: highlight.js
widgets: bootstrap
---

## Coursera Reproducible Pitch

### See the Regression Models Course Project  

- URL: *https://github.com/mykelsoftworld/developing-data-product/blob/main/Reproducible%20pitch.Rmd*
- Find here all the data that have been use for this presentation and also for the first part of the data Science Project: "First, you will create a Shiny application and deploy it on Rstudio's servers.Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application."

### Find all details here
URL: *https://https://www.coursera.org/learn/data-products/peer/tMYrn/course-project-shiny-application-and-reproducible-pitch*

---

## mtcars Dataset

### Motor Trend Car Road Tests

> The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).
### Source
> Henderson and Velleman (1981), Building multiple regression models interactively. Biometrics, 37, 391-411.
```{r comment=""}
library(datasets)
head(mtcars, 3)
```

---

## mtcars Dataset - Format

**A data frame with 32 observations on 11 variables.**

| Index | Field | Detail |
------- | ----- | ------ |
| [, 1] | mpg | Miles/(US) gallon |
| [, 2]  | cyl | Number of cylinders |
| [, 3]	| disp | Displacement (cu.in.) |
| [, 4]	| hp | Gross horsepower |
| [, 5]	| drat | Rear axle ratio |
| [, 6]	| wt | Weight (lb/1000) |
| [, 7]	| qsec | 1/4 mile time |
| [, 8]	| vs | V/S |
| [, 9]	| am | Transmission (0 = automatic, 1 = manual) |
| [,10]	| gear | Number of forward gears |
| [,11]	| carb | Number of carburetors |

---

## Analysis - Main Code

```{r}

mtcars$mpgsp <- ifelse(mtcars$mpg - 20 > 0, mtcars$mpg - 20, 0) 
    model1 <- lm(hp ~ mpg, data = mtcars)
    model2 <- lm(hp ~ mpgsp + mpg, data = mtcars)
    
 plot2 <- 
      
      plot(mtcars$mpg, mtcars$hp, xlab = "Miles Per Gallon", 
           ylab = "Horsepower", bty = "n", pch = 16,
           xlim = c(10, 35), ylim = c(50, 350))
     
        abline(model1, col = "red", lwd = 2)
      
    
        model2lines <- predict(model2, newdata = data.frame(
          mpg = 10:35, mpgsp = ifelse(10:35 - 20 > 0, 10:35 - 20, 0)
        ))
        lines(10:35, model2lines, col = "blue", lwd = 2)
      
      legend(25, 250, c("Model 1 Prediction", "Model 2 Prediction"), pch = 16, 
             col = c("red", "blue"), bty = "n", cex = 1.2)

   




    

```